---
title: "2 Subsetting"
author: "Lucas Shen"
date: "August 10, 2015"
output: html_document
---
> `str()` shows you the structure of any object, and **subsetting** allows you to pull out the pieces that you’re interested in.

##Data types
### 1. Atomic vectors
```{r}
x <- c(2.1, 4.2, 3.3, 5.4) # number after the decimal point gives the original position in the vector
```
***

####things you can use to subset a vector:

1. **positive integer** (what you want)
```{r}
x[c(3,1)]
x[order(x)] # order return sorted index, this line == sort(x)
x[c(1,1)] # return duplicate values
```
2. **negative integer** (what you don't want)
```{r}
x[-1]
```
3. **logical vector**
```{r}
x[c(TRUE, TRUE, FALSE, FALSE)]
x[x>3]
```
if logical vector is shorter than input vector, it will recycle to be the same length
```{r}
x[c(TRUE, FALSE)]
```
4. **nothing**, `x[]`: return original vector
5. **zero**, `x[0]`: return zero-length vector
6. **character vectors**, return elements with matching names
```{r}
y <- setNames(x, letters[1:4])
y[c("d", "c", "a")]
```
***

### 2. Matrices and arrays
```{r}
a <- matrix(1:9, nrow=3)
colnames(a) <- c('A', 'B', 'C')

a[1:2, ] # keep all colums
```

### 3. Data frames
```{r}
df <- data.frame(x=1:3, y=3:1, z=letters[1:3])
df[df$x ==2,] # take 2nd row
df[c(1,3), ] # take 1, 3 row
df[c('x', 'z')] # == df[, c('x', 'z')]
```
if only choose one colume,
```{r}
str(df['x']) # this subsetting would not simplify automatically
str(df[, 'x']) # auto simplify
```

notes inspired from exercise:

* `upper.tri()`
* `diag()`
```{r}
my_diag <- function(m){
  
}
```













