---
title: "5 functions"
author: "Lucas Shen"
date: "August 11, 2015"
output: html_document
---
***

```{r}
library(pryr)
library(dplyr)
```

#Function components
1. `body()`: the code inside the funciton
2. `formals()`: list of args
3. `environment()`: location of the map to the function's variables 

* `is.function()`
* `is.primitive()`

###exercise
```{r}
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)
```

> Which base function has the most arguments?

```{r}
# my realization is keep piping untill you have to make a temp var, I don't know if this is a good practice. We'll see
arg_length <- funs %>% sapply(function(x) length(formals(x))) # check this sapply use!
which(arg_length == max(arg_length)) %>% names() # check which
```

> How many base functions have no arguments? What’s special about those functions?

```{r}
no_arg_fn_name <- which(arg_length == 0) %>% names()
length(no_arg_fn_name)
```

> How could you adapt the code to find all primitive functions?

```{r}
objs %>% sapply(is.primitive) %>% sum() # this is answering how many
objs[objs %>% sapply("is.primitive")] %>% names() %>% head(10) # show up first 10 names of primitive fn
```

***

#Lexical scoping







