---
title: "5 functions"
author: "Lucas Shen"
date: "August 11, 2015"
output: html_document
---
***

```{r}
library(pryr)
library(dplyr)
```

#Function components
1. `body()`: the code inside the funciton
2. `formals()`: list of args
3. `environment()`: location of the map to the function's variables 

* `is.function()`
* `is.primitive()`

###exercise
```{r}
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)
```

> Which base function has the most arguments?

```{r}
# my realization is keep piping untill you have to make a temp var, I don't know if this is a good practice. We'll see
arg_length <- funs %>% sapply(function(x) length(formals(x))) # check this sapply use!
which(arg_length == max(arg_length)) %>% names() # check which
```

> How many base functions have no arguments? What’s special about those functions?

```{r}
no_arg_fn_name <- which(arg_length == 0) %>% names()
length(no_arg_fn_name)
```

> How could you adapt the code to find all primitive functions?

```{r}
objs %>% sapply(is.primitive) %>% sum() # this is answering how many
objs[objs %>% sapply("is.primitive")] %>% names() %>% head(10) # show up first 10 names of primitive fn
```

***
#Lexical scoping
> Lexical scoping looks up symbol values based on how functions were nested **when they were created**, not how they are nested when they are called. 

> With lexical scoping, you don’t need to know how the function is called to figure out where the value of a variable will be looked up. **You just need to look at the function’s definition**

###name masking
* The key is: **the context is decided at where the function is created**! However, for lousy code you may use varialbe that is in global scope and may depend on the runtime...
    * `codetools::findGlobals(fn_name)` -> lists all the external dependencies of a function

* for function name, it works the same on one caveat:

> if you are using a name in a context where it’s obvious that you want a function (e.g., f(3)), R will ignore objects that are not functions while it is searching.

###fresh start
> Every time a function is called, a new environment is created to host execution. A function has no way to tell what happened the last time it was run; each invocation is completely independent.

***

#Every operation is a function call

> “To understand computations in R, two slogans are helpful
>
> 1. Everything that exists is an object.
> 2. Everything that happens is a function call." 
>
> — John Chambers

```{r}
3 + 2
`+`(3, 2)

1:5 %>% sapply(`+`, 3) # with `+`, we pass the value of +, which is plus, into sapply
1:5 %>% sapply("+", 3) # here we pass the function name, +, not the function itself. sapply can magically handle these two situations.
```

***
#Function arguments
###call funciton
> Arguments are matched first by exact name (perfect matching), then by prefix matching, and finally by position.

* note: I would avoid using partial matching, and should not abuse positonal matching.

###calling fn with a list of args
```{r}
args <- list(1:10, na.rm = TRUE)
do.call(mean, list(1:10, na.rm = TRUE)) # == mean(1:10, na.rm = TRUE)
```

###missing arguments
> You can determine if an argument was supplied or not with the `missing()` function.

```{r}
miss <- function(x, y){
  c(missing(x), missing(y))
}

miss()
miss(1)
miss(1,1)
```

###lazy eval
> R function arguments are lazy — they’re only evaluated if they’re actually used
> Laziness is useful in if statements

```{r eval=F}
a <- NULL
if (is.null(a)) stop("a is null")
!is.null(a) || stop('a is null')
```

***
### ...
> could use `list()` to collect ... arguments

```{r}
f <- function(...) {
  names(list(...))
}
f(a = 1, b = 2)
```

***
#Special callls




















